The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-11-27 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments
Reorganize 'Options for nu' section

Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed data---often, a collection of polynomials or ideals---an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of the initial data).
Normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
The resulting limit, if it exists, should then encode some interesting information about the initial data.

@@

@@

We now describe the options available for the function \texttt{nu}.
As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}

In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
It is well known that, for any positive integer $e$,
\[ \nu_I^J(p^e) = \nu_I^J(p^{e-1})\cdot p + L,\]
where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.

@@

@@

>>>>

Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed data---often, a collection of polynomials or ideals---an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of the initial data).
Normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
The resulting limit, if it exists, should encode interesting information about the initial data.

@@

In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
It is well known that, for any positive integer $e$,
\[ \nu_I^J(p^e) = \nu_I^J(p^{e-1})\cdot p + L,\]
where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
% This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.

@@

@@

%We now describe the options available for the function \texttt{nu}.

@@

As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}
